### 2025-09-03 base-rates.qmd
20250903 - fix variable names

```{r}
rookiesDraftedEarly <- player_stats_seasonal %>% 
  filter(years_of_experience == 0) %>% 
  filter(draftround %in% c(1,2)) %>% 
  arrange(player_id, season) %>% 
  group_by(player_id) %>% 
  slice_head(n = 1) %>% 
  ungroup() %>% 
  mutate(
    rookie = 0,
    rookieLabel = "Rookie"
  ) %>% 
  arrange(player_display_name)

nonRookiesDraftedEarly <- player_stats_seasonal %>% 
  filter(years_of_experience > 0) %>% 
  filter(draftround %in% c(1,2)) %>% 
  mutate(
    rookie = 1,
    rookieLabel = "Non-rookie"
  ) %>% 
  arrange(player_display_name)

>>>>

```{r}
rookiesDraftedEarly <- player_stats_seasonal %>% 
  filter(years_of_experience == 0) %>% 
  filter(draft_round %in% c(1,2)) %>% 
  arrange(player_id, season) %>% 
  group_by(player_id) %>% 
  slice_head(n = 1) %>% 
  ungroup() %>% 
  mutate(
    rookie = 0,
    rookieLabel = "Rookie"
  ) %>% 
  arrange(player_display_name)

nonRookiesDraftedEarly <- player_stats_seasonal %>% 
  filter(years_of_experience > 0) %>% 
  filter(draft_round %in% c(1,2)) %>% 
  mutate(
    rookie = 1,
    rookieLabel = "Non-rookie"
  ) %>% 
  arrange(player_display_name)

### 2025-09-03 correlation.qmd
20250903 - fix variable names

```{r}
cor(
  player_stats_seasonal[,c("draftround","fantasyPoints")],
  use = "pairwise.complete.obs",
  method = "spearman")

cor.test(
  ~ draftround + fantasyPoints,
  data = player_stats_seasonal,
  method = "spearman"
)
```

@@

spearman_test <- cor.test(
  ~ draftround + fantasyPoints,
  data = player_stats_seasonal,
  method = "spearman"
)

spearman_r <- spearman_test$estimate
spearman_df <- cor.test(
  ~ draftround + fantasyPoints,
  data = player_stats_seasonal)$parameter
spearman_p <- spearman_test$p.value
```

@@

```{r}
psych::partial.r(
  data = player_stats_seasonal,
  x = c("draftround","fantasyPoints"),
  y = "age",
  method = "spearman"
)
```

@@

correlation::correlation(
  data = player_stats_seasonal %>% select(draftround, fantasyPoints),
  method = "distance"
)
```

>>>>

```{r}
cor(
  player_stats_seasonal[,c("draft_round","fantasyPoints")],
  use = "pairwise.complete.obs",
  method = "spearman")

cor.test(
  ~ draft_round + fantasyPoints,
  data = player_stats_seasonal,
  method = "spearman"
)
```

@@

spearman_test <- cor.test(
  ~ draft_round + fantasyPoints,
  data = player_stats_seasonal,
  method = "spearman"
)

spearman_r <- spearman_test$estimate
spearman_df <- cor.test(
  ~ draft_round + fantasyPoints,
  data = player_stats_seasonal)$parameter
spearman_p <- spearman_test$p.value
```

@@

```{r}
psych::partial.r(
  data = player_stats_seasonal,
  x = c("draft_round","fantasyPoints"),
  y = "age",
  method = "spearman"
)
```

@@

correlation::correlation(
  data = player_stats_seasonal %>% select(draft_round, fantasyPoints),
  method = "distance"
)
```

### 2025-09-03 multiple-regression.qmd
20250823 - fix error
20250903 - fix variable names

dataToImpute <- player_stats_seasonal %>% 
  filter(position %in% c("WR")) %>% 
  select(player_id, position, where(is.numeric)) %>% 
  select(
    player_id:games, carries:wopr, fantasy_points, fantasy_points_ppr,
    rush_40_yds, rec_40_yds, fumbles, two_pts, return_yds,
    rush_100_yds:draftround, height:target_share_log) %>% 
  select(-c(fantasy_points_ppr, ageCentered20, target_share_log)) # drop collinear variables

@@

imp_long$fantasyPoints_transformed <- predict(
  yjTransformed,
  newdata = imp_long["fantasyPoints"])$fantasyPoints

@@

>>>>

dataToImpute <- player_stats_seasonal %>% 
  filter(position %in% c("WR")) %>% 
  select(player_id, position, where(is.numeric)) %>% 
  select(
    player_id:games, carries:wopr, fantasy_points, fantasy_points_ppr,
    rush_40_yds, rec_40_yds, fumbles, two_pts, return_yds,
    rush_100_yds:draft_round, height:target_share_log) %>% 
  select(-c(fantasy_points_ppr, ageCentered20, target_share_log)) # drop collinear variables

@@

imp_long$fantasyPoints_transformed <- predict(
  bnTransformed,
  newdata = imp_long[["fantasyPoints"]])

@@

mice::pool(imp_regression)
